### 2013-07-28 patchy-selection-paper.tex
more plots

@@

>>>>

\begin{figure}[ht!]
  \begin{center}
    \includegraphics{sim-snapshots}
  \end{center}
  \label{fig:sim_snapshots}
  \caption{
  Results from individual-based simulation, on a one-dimensional grid:
  the focal allele is beneficial in the central 20 demes, with $s_b=0.1$,
  and deleterious elsewhere, with $s_m=-0.02$.
  The dynamics were simulated for 10000 generations; demes had 1000 individuals in each;
  dispersal was to nearby demes with a mean dispersal distance of $\sigma \approx 1.66$  times the deme spacing.
  \textbf{(A)} Allele frequencies across space: colored lines are snapshots at an evenly spaced set of times,
  and the solid lines shows the cumulative mean occupation frequency across all generations.
  \textbf{(B)} A segment of the temporal dynamics: space is again shown across the horizontal axis;
  with time on the vertical axis; demes are colored darker red the greater then allele frequency at the corresponding time.
  The 50\% and 5\% frequency contour lines are in grey,
  and the genealogy of 50 individuals in a rare long-distance excursion is traced back with black lines.
  }
\end{figure}

@@

\begin{figure}[ht!]
  \begin{center}
    \includegraphics{sim-occupation-freqs}
  \end{center}
  \label{fig:sim_occupation_freqs}
  \caption{
  Mean occupation frequencies from simulation; details are as in figure~\ref{fig:sim_snapshots} except as otherwise noted.
  Each panel shows mean occupation frequencies of individual demes (grey dots)
  and averaged over demes at similar distances (black circles), on
  \textbf{(A)} a one-dimensional grid of 150 demes, and
  \textbf{(B)} a two-dimensional grid of $50\times 50$ demes.
  Superimposed in black is the decay predicted by \eqref{eqn:eqfreq} (with $C=1/2$).
  The two distinct lines of grey points in (A) are to the left and right of the patch, respectively.
  }
\end{figure}
